---
title: "Developing Data Products, Leaflet Project"
author: "Ruben_Mkrtchyan"
date: "18/05/2021"
output:
  ioslides_presentation: default
---
About the Project {.upper}
==========================================================================
Here is my Leaflet project of Developing Data Products course provided by John Hopkins University. In this short project you can find the 'big six' football clubs of English Premier League in the map. The location of those clubs' stadiums are showed by their corresponding logos. Moreover, you can visit the official website of those clubs through the link which will appear when you click on the logo. For your information, the 'big six' clubs are considered the best six clubs of EPL and those are Arsenal, Chelsea, Tottenham Hotspur, Manchester United, Manchester City and Liverpool. 

The Map of "Big Six" clubs of EPL 
==========================================================================

```{r echo = FALSE, message = FALSE, include = FALSE, warning=FALSE}
#install.packages('leaflet')
```

```{r echo = FALSE, message = FALSE, warning=FALSE, fig-margin, fig.margin=TRUE}
library(leaflet)
defaultW <- getOption("warn") 
options(warn = -1) 
options(warn = defaultW)

Team_Icons <- makeIcon(iconUrl = c('http://icons.iconseeker.com/png/fullsize/soccer-teams/arsenal-fc-logo.png', 'https://quretic.com/DLS/chelsea%20logo.png', 'http://futhead.cursecdn.com/static/img/14/clubs/18.png', 'https://dlscenter.com/wp-content/uploads/2017/06/manchester-united-escudo.png', 'https://quretic.com/DLS/Manchester%20City%20logo.png', 'https://www.mucizeli.com/wp-content/uploads/2019/09/logo-1.png'), iconWidth = 31*215/230, iconHeight = 31, iconAnchorX = 31*215/230/2, iconAnchorY = 16)

Team_Sites <- c("<a href='https://www.arsenal.com/'> Arsenal London FC</a>", "<a href='https://www.chelseafc.com/en'> Chelsea FC</a>","<a href= 'https://www.tottenhamhotspur.com/'> Tottenham Hotspur FC</a>","<a href= 'https://www.manutd.com/'> Manchester United FC</a>","<a href= 'https://www.mancity.com/'> Manchester City FC</a>","<a href= 'https://www.liverpoolfc.com/'> Liverpool FC</a>")

df <- data.frame(lat = c(51.5549, 51.481667, 51.603333, 53.463056, 53.482989, 53.430819), lng = c( -.1084, -0.191111, -0.065833, -2.291389, -2.200292, -2.960828))

df %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = Team_Icons, popup = Team_Sites)
```
